\pkg{pksensi}: An R package to apply sensitivity analysis in pharmacokinetic models

### 2019-06-24 manuscript/manuscript.Rmd
APAP

The aim of this section is to reproduce our previous published result \citep{fphar201800588} of global sensitivity analysis for acetaminophen PBPK model through \pkg{pksensi}. The model codes are included in this package and can be generated through \code{pbpk_apap_model()}. We applied the global sensitivity analysis workflow to the original published model with 21 model parameters [@s13318-015-0253-x]. The descriptions of each parameter and the sampling ranges are list in Table 1.

@@

```{r, eval=T}
mName <- "pbpk_apap"
pbpk_apap_model()
compile_model(mName, application = "mcsim")
```

>>>>

The aim of this section is to reproduce our previous published result \citep{fphar201800588} of global sensitivity analysis for acetaminophen PBPK model through \pkg{pksensi}. The model codes are included in this package and can be generated through \code{pbpk_apap_model} function. We applied the global sensitivity analysis workflow to the original published model with 21 model parameters [@s13318-015-0253-x]. The descriptions of each parameter and the sampling ranges are list in Table 1.

@@

```{r, eval=T}
mName <- "pbpk_apap"
pbpk_apap_model()
compile_model(mName, application = "mcsim", version = "6.1.0")
```
